---
title: "Parallel Worlds"
author: "Francesco Prem Solidoro, Michele Salvi"
format:
  typst:
    toc: true
    section-numbering: 1.1.a
    columns: 1
execute:
  warning: false
editor: visual
---

# Parallel Worlds - a View of Social Media Manipulation and Polarization

```{r}
library(tidyverse)
library(paletteer)
library(ggthemes)
library(knitr)
library(psych)
library(readr)
library(ggpmisc)
library(tidytext)
library(tm)
library(gridExtra)
```

## Importing, merging and cleaning the dataset

We got the following datasets from [538's github](github.com/fivethirdyeight/russian-troll-tweets). Analysis will be performed using the NRD, bing and afinn lexicons

```{r}
IRAtweets1 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_1.csv")
IRAtweets2 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_2.csv")
IRAtweets3 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_3.csv")
IRAtweets4 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_4.csv")
IRAtweets5 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_5.csv")
IRAtweets6 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_6.csv")
IRAtweets7 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_7.csv")
IRAtweets8 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_8.csv")
IRAtweets9 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_9.csv")
IRAtweets10 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_10.csv")
IRAtweets11 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_11.csv")
IRAtweets12 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_12.csv")
IRAtweets13 <- read_csv("data/russian-troll-tweets/IRAhandle_tweets_13.csv")

df_list <- list(
              IRAtweets1,
              IRAtweets2,
              IRAtweets3,
              IRAtweets4,
              IRAtweets5,
              IRAtweets6,
              IRAtweets7,
              IRAtweets8,
              IRAtweets9,
              IRAtweets10,
              IRAtweets11,
              IRAtweets12,
              IRAtweets13
)

IRAtweets <- do.call("rbind", df_list)
IRAtweets <- subset(IRAtweets, select=c(-external_author_id,-harvested_date,-new_june_2018,-alt_external_id,-tweet_id,-article_url,-tco1_step1,-tco2_step1,-tco3_step1))

set.seed(777)
```

Since the analysis is quite taxing, we're going to sample 100.000 tweets to perform a preliminary analysis on. Remove the first line in the following block in order to conduct an analysis of the full dataset.

```{r}
IRAtweets <- IRAtweets[sample(nrow(IRAtweets), 100000),] #remove line for complete analysis 
head(IRAtweets)
```


